The shape of kelp: environmental influences on kelp morphology

### 2018-09-10 chapter_2.Rmd
minor edits and additions

---
title: "The shape of kelp: environmental influences on kelp morphology"
output:
  word_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    highlight: zenburn
    toc: no
  html_notebook:
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
  bookdown::html_document2:
    fig_caption: yes
    fig_retina: 2
    fig_width: 7
    highlight: espresso
    theme: sandstone
    toc_float: no
fontsize: 12pt
geometry: margin=1in
language: Australian
mainfont: PT Serif
monofont: PT Mono
csl: LaTeX/ecography.csl
papersize: A4
sansfont: PT Sans
tables: yes
bibliography: LaTex/mycollection.bib
---

>>>>

---
title: "The shape of kelp: environmental influences on kelp morphology"
output:
  word_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    toc: no
  html_notebook:
    fig_caption: yes
    toc: yes
  pdf_document:
    toc: yes
  bookdown::html_document2:
    fig_caption: yes
    fig_retina: 2
    fig_width: 7
    highlight: espresso
    theme: sandstone
    toc_float: no
fontsize: 12pt
geometry: margin=1in
language: Australian
mainfont: PT Serif
monofont: PT Mono
csl: LaTeX/ecography.csl
papersize: A4
sansfont: PT Sans
tables: yes
bibliography: LaTex/mycollection.bib
---
